---
title: "flood events division"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{flood_division}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(FloodR)
```

# 洪水事件划分

## Separation of flood events

For the separation of flood events from a discharge timeseries, we need the daily discharge. 
```{r}
date_begin = as.Date("01.01.2000", format = "%d.%m.%Y")
date_end = as.Date("01.01.2004", format="%d.%m.%Y")

df_q <- data.frame(
  Date = seq(date_begin, date_end, "day"),
  discharge = rbeta(1462, 2, 20)*100) # dummy data
flood_events <- eventsep(df_q)
head(flood_events)
```

The Separation might still contain overlaid flood events which need to be corrected.

## 参数的选择



## Correction of flood events

Run the Web separation on the dummy Catchment
As input to the function a minimum of discharge data is used. The Flood event tables can be opened from within the User-Interface
```{r, eval = FALSE}
Run_WebFlood()
```

# 洪水事件的类型


### Typing of flood events

For the typing of the flood event, multiple characteristics for each flood event must be calculated before:

* Sum_SM: Sum of snowmelt during the floodevent in mm

* Sum_N: Sum of precipitation during the floodevent in mm (For example from the separation of precipitation)

* dir_Volume: Direct volume of the flood event (Volume minus baseflow) in Mio. m³/s (This is calculated in the floodevent separation as well as in the output after running the Run_WebFlood)

* HQ_dir: Direct peak (instantaneous flood peak minus baseflow) in m³/s (This is calculated in the floodevent separation as well as in the output after running the Run_WebFlood)

* PSI_SM: Runoff coefficient of the flood event with snowmelt + precipitation

```{r}
# Open the sample flood event data
data("Sample_Flood_events")
head(Sample_Flood_events)

# Run the event typing
Floods_typed <- Flood_typology(Floods = Sample_Flood_events, n_G = 3, Type_3_min_samplesize = 10)

table(Floods_typed$Type)

# Plot the event typing
Floods_Rain <- Floods_typed[Floods_typed$Type %in% c("R1", "R2", "R3"),]

library(ggplot2)
ggplot(Floods_Rain)+
  geom_point(aes(x=dir_Volume, y=HQ_dir, fill=Type), 
    colour="black", shape=21, size=2)+
  scale_fill_manual(values = c("R1"="#D7191C", "R2"="#FDAE61", "R3"= "#1A9641"))
```
